Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-17 paper.qmd
Added error categories

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = emb1,
             y = emb2,
             colour = sqrt_row_wise_total_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  xlab("tSNE1") +
  ylab("tSNE2") +
  theme_bw() +
  theme(
    aspect.ratio = 1,
    legend.position = "none"
  )

error_plot_two_curvy_quasi <- ggplot(
  error_df_two_curvy_abs, 
  aes(x = sqrt_row_wise_total_error, 
      y = 0, 
      colour = sqrt_row_wise_total_error)) +
  geom_quasirandom(alpha = 0.5) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  xlab(expression(e[hj])) +
  ylab("") +
  theme_bw() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none")
```

@@

>>>>

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = emb1,
             y = emb2,
             colour = error_cat)) +
  geom_point(alpha=0.5) +
  scale_colour_manual(values = c("#FFFFC8", "#FFFAC0", "#FEF2B3", "#FCE9A3",
                                 "#FADE8F", "#F9D378", "#F8C65D", "#F6B938",
                                 "#F5AA00", "#F49B00", "#F28A00", "#F07800",
                                 "#ED6400", "#EA4D00", "#DE3900", "#CD2A00",
                                 "#BB1B00", "#A70C00", "#93001C", "#7D0025")) +
  xlab("tSNE1") +
  ylab("tSNE2") +
  theme_bw() +
  theme(
    aspect.ratio = 1,
    legend.position = "none"
  )

error_plot_two_curvy_quasi <- ggplot(
  error_df_two_curvy_abs, 
  aes(x = sqrt_row_wise_total_error, 
      y = 0, 
      colour = error_cat)) +
  geom_quasirandom(alpha = 0.5) +
  scale_colour_manual(values = c("#FFFFC8", "#FFFAC0", "#FEF2B3", "#FCE9A3",
                                 "#FADE8F", "#F9D378", "#F8C65D", "#F6B938",
                                 "#F5AA00", "#F49B00", "#F28A00", "#F07800",
                                 "#ED6400", "#EA4D00", "#DE3900", "#CD2A00",
                                 "#BB1B00", "#A70C00", "#93001C", "#7D0025")) +
  xlab(expression(e[hj])) +
  ylab("") +
  theme_bw() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none",
        plot.margin = margin(0, 0, 0, 0))
```

@@

projected_df <- proj_obj1$projected_df
axes <- proj_obj1$axes
circle <- proj_obj1$circle
cluster <- proj_obj1$cluster

projected_df <- projected_df |>
      dplyr::mutate(cluster = proj_obj1$cluster)

two_curvy_proj_tsne_first_model1_coloured <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2,
      colour = cluster)) +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  scale_colour_manual(values = c("#FFFFC8", "#FFFAC0", "#FEF2B3", "#FCE9A3",
                                 "#FADE8F", "#F9D378", "#F8C65D", "#F6B938",
                                 "#F5AA00", "#F49B00", "#F28A00", "#F07800",
                                 "#ED6400", "#EA4D00", "#DE3900", "#CD2A00",
                                 "#BB1B00", "#A70C00", "#93001C", "#7D0025")) +
  xlim(c(-0.6, 0.6)) +
  ylim(c(-0.6, 0.6)) +
  theme(aspect.ratio = 1,
        legend.position = "none")
